Diffantom: a software layer to build digital phantoms of whole-brain diffusion MRI

### 2015-07-23 paper/main.tex
fix missing references to FAST and FIRST

\glsresetall
\linenumbers
\section*{Appendix}\label{sec:appendix}
Let $\{T'_{1\,\cdots\,5}\}$ be the set of original fractions maps obtained with the combined use of FAST and FIRST, FA the
  \gls*{fa} map obtained from the original \gls*{dmri} data, and $\{V_{1\,\cdots\,3}, F'_{1\,\cdots\,3}\}$ the direction
  maps $V_i$ of restricted diffusion by fibers with their estimated volume fractions $F'_i$ calculated with BEDPOSTX.
The final $\{T_{1\,\cdots\,5}\}$ maps of isotropic fractions are computed as follows:

>>>>

\glsresetall
\linenumbers
\section*{Appendix}\label{sec:appendix}
Let $\{T'_{1\,\cdots\,5}\}$ be the set of original fractions maps obtained with \texttt{act\_anat\_prepare\_fsl}, a
  tool in \emph{MRTrix} that combines FAST \citep{zhang_segmentation_2001} and FIRST \citep{patenaude_bayesian_2011}
  to generate the macrostructural 5TT map.
FA denotes the \gls*{fa} map obtained from the original \gls*{dmri} data, and $\{V_{1\,\cdots\,3}, F'_{1\,\cdots\,3}\}$ the direction
  maps $V_i$ of restricted diffusion by fibers with their estimated volume fractions $F'_i$ calculated with BEDPOSTX.
The final $\{T_{1\,\cdots\,5}\}$ maps of isotropic fractions are computed as follows:
